\begin{rubric}{\color{Maroon}Publications}
\entry*[] Godase, D. G. and \textbf{\color{Maroon}Mahadik, S. B.} (2019). The SPRT control chart for process dispersion. \textit{Quality and Reliability Engineering International}, DOI: 10.1002/qre.2481.
\vspace{0.12cm}
%
\entry*[]  \textbf{\color{Maroon}Mahadik, S. B.} (2017). A unified approach to adaptive Shewhart control charts. \textit{Communications in Statistics-Theory and Methods}, 46(20), 10272-10293.
\vspace{0.12cm}
%
\entry*[]  \textbf{\color{Maroon}Mahadik, S. B.} (2015) ‘A simultaneous evaluation of adaptive design
parameters policies for Hotelling’s 2 T charts’, \textit{International Journal of Science, Engineering and Technology Research}, Vol 4, pp. 3936-3944.
\vspace{0.12cm}
%
\entry*[]  \textbf{\color{Maroon}Mahadik, S. B.} (2014) ‘X charts with variable sampling interval, control limits, and warning limits’, \textit{International Journal of Engineering Research \& Technology}, Vol 3, pp. 615-620.
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} (2014) ‘Hotelling’s 2 T charts with variable sample size, sampling interval, and warning limits’, \textit{International Journal of Science, Engineering and Technology Research}, Vol. 3, No. 1, pp. 41-54.
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} (2013) ‘ X charts with variable control and warning limits’, \textit{Economic Quality Control}, Vol 28, No. 2, pp. 117-124.
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} (2013) ‘Variable sample size and sampling interval Hotelling’s 2 T charts with runs rules for switching between sample
sizes and sampling interval lengths’, \textit{International Journal of
	Reliability, Quality and Safety Engineering}, Vol. 20, No. 4, DOI:
10.1142/S0218539313500150
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} (2013) ‘ X charts with variable sampling interval and warning limits’, \textit{Journal of Academia and Industrial Research}, Vol 2,
No. 2, pp. 103-110.
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} (2013) ‘Hotelling’s 2 T charts with variable sampling interval and warning limits’, \textit{International Journal of Quality
	Engineering and Technology}, Vol 3, No. 4, pp. 289-302.	
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} (2013) ‘Variable sample size and sampling interval X charts with runs rules for switching between sample sizes and
sampling interval lengths’, \textit{Quality and Reliability Engineering
	International}, Vol 29, No.1, pp. 63-76.
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} (2012) ‘Hotelling’s 2 T charts with variable control and warning limits’, \textit{International Journal of Quality Engineering and Technology}, Vol 3, No. 2, pp. 158-167.
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} (2012) ‘ X charts with variable sample size, sampling
interval, and warning limits’, \textit{Quality and Reliability Engineering
	International}, Vol 29, No. 4, pp. 535-544.
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} (2012) ‘Variable sampling interval Hotelling’s 2 T charts with runs rules for switching between sampling interval
lengths’, \textit{Quality and Reliability Engineering International}, Vol. 28 No. 2, pp. 131-140.
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} (2012) ‘Exact results for variable sampling interval Shewhart control charts with runs rules for switching between
sampling interval lengths’, \textit{Communications in statistics – Theory and
	Methods}, Vol. 41 No. 24, pp. 4453-4469.
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} and Shirke, D. T. (2011) ‘A special variable sample size and sampling interval Hotelling’s 2 T chart’, \textit{The International Journal of Advanced Manufacturing Technology}, Vol. 53 Nos. 1-4, pp. 379-384.
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} and Shirke, D. T. (2009) ‘A special variable sample size and sampling interval X chart’, \textit{Communications in Statistics – Theory and Methods}, Vol. 38 No. 8, pp. 1284-1299.
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} and Shirke, D. T. (2007) ‘Economic design of a modified variable sample size and sampling interval X chart’,
\textit{Economic Quality Control}, Vol. 22, pp. 273-293.
\vspace{0.12cm}
%
\entry*[] \textbf{\color{Maroon}Mahadik, S. B.} and Shirke, D. T. (2007). On superiority of a variable sampling interval control chart. Journal of Applied Statistics, Vol. 34 No. 4, pp. 443-458.
\end{rubric}